### 2020-12-22 msc-thesis.tex
New structure

          \vspace{0.5\baselineskip}
          {
               \huge
               \textbf{Messaging Architecture for Integration of Identity Management Systems}
          }

@@

The result is a digital identity crisis \cite{IdentityCrisis}:
\begin{itemize}
    \item Multiple SPs collect, use and share parts of identities which leads to a distributed and fragmented identity.
    \item As a result of the distributed identity, risk of data breaches increases.
    \item Managing multiple use profiles is very inconvenient for users.
    \item It is often unclear who stores which data and for what purpose.
    \item SPs have an incentive to collect and share more user data than they need, to provide their service.
\end{itemize}

@@

\begin{itemize}
    \item OZG scenarios are based on documented digitalization efforts of administrative services in the context of the OZG and are for example be the application for an administrative service or the communication with a governmental institution.
    \item The system architecture is based on documentation about architecture plans of member states.
    \item The functionalities of the IMP are based on a requirements analysis of OZG scenarios and additional research.
    \item The connector is defined based on functionalities the integration architecture requires from the IMP.
    \item The integration architecture is the main scientific contribution of this bachelor thesis. It is based on messaging patterns in order to utilize a combination of established and tested messaging solutions. In order to save investments it also reuses as many system components as possible and modifies as few system components as necessary.
\end{itemize}

\chapter{Structure of Work}
In the beginning of the thesis, terminology and basic concepts are explained.
This includes definitions of terms like Online Self-Service, Identity and Identity Management. The concept of Identity Management Providers and the Online Access Law are explained. The special relevance for integration of IMPs and OZG are described.

Then, preparatory work relevant for the integration architecture is presented. Relevant OZG scenarios based on digitisation documentations of administrative services are analyzed in order to define important features the IMP is required to have. The connector which makes the IMP accessible towards the integration architecture is documented. Based on documentation of system architectures of several member states, relevant components of the architecture relevant for the OZG are selected. Each component is explained in detail along with the functionalities it provides for usage by the integration architecture.

The integration architecture integrates previously documented connector and components of the system architecture in order to make selected OZG scenarios usable with the IMP. The architecture is presented iterative. Each iteration contains increasingly demanding requirements along with the documentation of the increasingly complex integration architecture. Each documentation is done through textual explanations, multiple flow diagrams and one messaging architecture.

In order to validate the integration architecture, the execution of one administration service with usage of the IMP is evaluated in theory.

@@

\subsection{Service Provider}
Service providers (SP) are entities like enterprises or organisations which make services accessible over the internet.

\subsection{Online Self-Service}
Online self-service (OSS) describes a method used by Service Providers to make their services available to the user. The method is characterized by being available over the internet, requiring no direct human interaction but instead enabling the user to access services in a self-reliant way. The user is usually supported by a variety of software solutions.

\subsection{Self-Service Tools}
Self-service tools are software solutions for customers to enable a online self-service experience. Depending on the use case, the tools can be transactional or informing. Informing tools help users to retrieve relevant information, often replacing human customer support. Transactional tools help users to interact with services in a persistent way to for example save personal data or trigger business processes.

@@

\subsection{Digital Identity}
The digital identity, for simplicity called identity in the thesis, is the sum of all digital personal information. This includes a set of identifiers which are pieces of information that can uniquely identify an entity and attributes which describe properties of an entity but do not uniquely identify it. It is also possible to use an aggregation of attributes as identifier.

@@

\subsection{Partial Digital Identity}
A partial digital identity is a subset of an identity. Partial identities are commonly used by SPs to manage identity information which is relevant for them.

\subsection{Identity Management}
Identity management is the creation, utilization / reading , updating and deletion of identities or partial identities. The possible utilization of identities depends on the system for management of identities. It could be for example authorization for a service or communication through an inbox.

\subsection{Identity Management System}
Identity management systems are solutions which enable SPs and customers to manage identities.

\subsection{User Profile}
User profiles are one method for identity management. They are characterized by each SP providing a separate identity management system which often consist of an identity provider (IdP) for storing identities, a customer relation management system (CRM) for accessing identities internally and a website with online self-service tools for providing access to customers.

\section{Digital Identity Crisis}
The current situation of digital identities has the following core issues:
\begin{itemize}
    \item aktuelle übersicht über identitiy management
    \begin{itemize}
        \begin{itemize}
            \item oAuth
            \item saml
        \end{itemize}
        \item Social Login
        \item central idps
        \item idendity federation (SOcial login, Single sign on)
        \item device identity kopplung
        \item SSI
    \end{itemize}
\end{itemize}

\section{Identity Management Provider}
Identity management providers (IMP) are a method for identity management which aims to solve the digital identity crisis. They are characterized by giving SPs access to customer identities for which they provide one-stop online self-service. The important aspect of IMP is, that the identity is stored and managed in one place and its utilization is enabled through integration with system architectures of multiple SPs.

\subsection{Objective}
The IMP method can solve the identity issues the following way:

\subsection{IMP System}
A system for IMP can work as follows:

Additional requirements for IMP systems can exist and are analyzed as part of the preparatory work.

\subsection{Integration}
The IMP system has to be integrated. A connector is used:

\subsection{Challenges}
The IMP system has the following problems / open questions regarding integration:
\begin{itemize}
    \item which personal information resides at SP systems an which at IMP systems? => data the user personally manages resides at IMP systems, derived data etc. at SP systems
    \item should data be mirrored at the SP and just a synchronisation functionality exist
\end{itemize}

\section{Online Access Law}
The Federal Ministry of the Interior, Building and Community is, amongst other things, responsible for modernizing public administration \cite{BMI:Moderne_Verwaltung}. Current modernization efforts lie in the construction of an E-Government \cite{BMI:Behoerdengaenge}.
The E-Government-Law in 2013 was an early step increasing internal usage of digital systems in governmental administration. This includes for example the usage of digital personal files and scanning of documents for replacement \cite{BMI:E-Government_Gesetz}. 
In 2017 the German government passed the law for improvement of online access to administrative services (OZG) which focuses on usage of administration services by the people \cite{BMI:Onlinezugangsgesetz}. 
Modernization of the administration, however, is not exclusive to Germany as in 2018 the European Parliament and Council decided on a Single Digital Gateway (SDG) providing uniform access to digital administrative governmental services of every European country \cite{BMI:Single_Digital_Gateway}.

Customers on the free market are used to One-Stop-Shops providing access to services of companies in one digital place. Many self-service methods improve the user experience: Customers of e-commerce companies can put products in a digital shopping card, pay with digital money and select a location for delivery. In most cases, no direct human to human interaction is required. Customers complete the process of ordering in self-service. The progress of online self-service usage on the free market is a result of the ongoing digitalization of the world and the competitiveness of the market. Today, many customers own personal computers or smartphones and companies providing easy access to their services via online self-service have an advantage in the market.
Governmental institutions provide administrative services for customers. This can for example be an application for child benefit or a new ID card. In contrast to the free market, access to administrative services is, in most cases, not available through online self-service. Reasons are, that digitalization is expensive and governmental institutions do not have competitors.
Digitalization of governmental administration could for example enable users to inform themselves about available administrative services and access them over the internet. The need to personally appear in offices of an administration would be reduced. Communication about questions or required documents could also happen faster, more immediate, and more reliable over the internet than over mail. Governmental institutions could reduce bureaucracy through modernization of registries and the once-only principle.
The German government recognizes the possible improvements and presents, amongst other things, the OZG as a solution. \cite{IT-Planungsrat:Herausforderung}

The law for improvement of online access of administrative services (Online Access Law - OZG) passed in 2017 and requires federal republic and member states to execute the following regulations until 2022 \cite{BMI:OZG_Wortlaut}:
\begin{enumerate}
    \item \textbf{Digital availability of administrative services} \\
    An administrative service is the electronic processing of administrative procedures which are available from outside the governmental institution.  As it is not clear which administrative services exactly are meant by the definition of the OZG, the BMI created a catalogue \cite{BMI:Verwaltungsleistungen}. The OZG requires these services to be digitally available. As a guideline to what is considered sufficient availability, the BMI defined a maturity model \cite{BMI:Digitale_Services}.
    \item \textbf{Digital access to administrative services through administration portals of a portal network} \\
    Federal republic, each member state and each commune must provide an administration portal. Portals of communes must be linked to the portal of the corresponding member state. Portals of federal republic and member states must be connected through a portal network. \cite{BMI:Portalverbund} Each portal must provide a "seek and find" feature, which enables users to find all administrative services provided by any administration portal \cite{Cotar:Drucksache_19/19089}. 
    \item \textbf{Interoperable user profiles for accessing administrative services} \\
    Federal republic and member states must provide user profiles which can be used to identify the corresponding person while requesting access to administrative services, to save personal information according to the once-only principle, to receive and send messages via a digital mailbox and to pay for services \cite{Cotar:Drucksache_19/19089}. The user profiles must be interoperable for every administration portal of the portal network.
\end{enumerate}

Execution of the OZG can be separated into two projects: Digitalization and Networking. Digitalization focuses on transformation of existing processes and services to be using modern technologies. This includes most importantly the digitalization of governmental administrative services. The networking focuses on connecting existing and future governmental systems to make digitalization universally usable. This includes most importantly the construction of administration portals which are connected in a portal network.

Many services, which are still bound to paper must be digitized. In total, the BMI lists 575 relevant services. Some of them are provided by the federal republic, some by the member states and yet other by the communes. Respective to these responsibilities, the task of digitalization is distributed between federal republic and member states, where each member state is assigned to take the lead for specific areas. \cite{BMI:Onlinezugangsgesetz} Results of the digitalization are documented on the "OZG-Informationsplattform" \cite{BMI:Informatiosplattform} as process diagrams and data schemata.

Administrative services are made available through administrative portals which are be provided by federal republic, each member state and each commune. Communes integrate their portals with corresponding member states. The portals are connected through an "Online-Gateway" and form a portal network.

Federal republic and each member state provide digital access to administrative services. An important method is called "one for all": One member state manages the digitalization of a category of administrative services and makes them digitally accessible for every other member state. Every administrative service can be found through a search function provided by every portal of the network.

Depending on the administrative service, a user profile is required to verify ones identity. As federal republic and most member states already provide their own user profiles, the "IT-Planungsrat" decided to save investments by connecting them to an interoperable user profile.

There exists a low, substantial and high level of authentication security when logging in to a user profile or when creating one.
A low trust level is for example the usage of a username and password combination, a high trust level is for example the usage of the eID feature of the German ID card. Depending on the administrative service a profile tries to access, a different trust level is required.

Profiles also enable users to save personal data in a data wallet and to communicate with institutions through an inbox.

The OZG is a fitting example for integration of IMP solutions and could benefit from it because:

\chapter{Preparatory Work}

\section{OZG Processes}

\begin{itemize}
    \item selecting important processes (priority 1)
    \item describing processes: purpose, result, etc
    \item process diagram visualizing
    \item 
\end{itemize}

\section{OZG Scenarios}

\begin{itemize}
    \item structuring parts of upper processes into clusters
    \item 
\end{itemize}

@@

\subsection{Identity Management}

\subsubsection{Scenario Profile Management}
\begin{itemize}
    \item Create a user profile
    \item Delete a user profile
    \item Check existence of a user profile
\end{itemize}

\subsubsection{Scenario Identity verification}
\begin{itemize}
    \item Login to a user profile
    \item Provide multiple levels of security for identity verification
    \item Usage of a guest profile
\end{itemize}

\subsection{Request Management}

\subsubsection{Scenario Request Preparation}
\begin{itemize}
    \item Search for administration services
    \item Check necessity of a profile
    \item Check required level of identity verification
    \item Selection of institution responsible for processing the request (Specification of current location)
\end{itemize}

\subsubsection{Scenario Request Creation}
\begin{itemize}
    \item Filling in a form for an application
    \item Automated filling in of form with saved personal data
    \item Collaboration on application by multiple identities
\end{itemize}

\subsubsection{Scenario Request Delivery}
\begin{itemize}
    \item Transmission of an application to responsible institution
\end{itemize}

\subsubsection{Scenario Request Processing}
\begin{itemize}
    \item Period of validity of applications
    \item Notification of user about missing information or documents
    \item Transmission of missing information
    \item Notification of user about required preliminary administration services
    \item Communication through E-Mail
    \item Cancel an application
    \item Approvals of user to e.g. data protection or information transfer
    \item Modification request of application after transmission
    \item Notification of received application by institution
    \item Request status update by user
    \item Sending notification to confirm the reading of a message
    \item Notification of certain events to separate person e.g. parents
    \item Request of institution about explicit document
\end{itemize}

\subsubsection{Scenario Request Finalization}
\begin{itemize}
    \item Notification of outcome of process / application
    \item Objection of user to result of the process
    \item Access to signed digital formula of result of process
    \item Definition of dates for evens
\end{itemize}

\subsection{Data Management}

\subsubsection{Scenario Access Management}
\begin{itemize}
    \item Access to an application by multiple separate identities
    \item Sharing of documents saved in a wallet
\end{itemize}

\subsubsection{Scenario Data Consistency}
\begin{itemize}
    \item Period of validity of documents
    \item Profile data discrepancies between involved user profiles
\end{itemize}

\subsubsection{Scenario Data Accessibility}
\begin{itemize}
    \item Upload of e.g. documents and certificates
    \item Saving personal data entered in a form to the user profile
    \item Protocol of all processes accessible with information about interactions
\end{itemize}

\section{OZG System Architecture}
This section describes the system architecture of a member state relevant for the execution of the OZG and integration of an IMP. Due to a lack of detailed information, the system architecture is described by components responsible for a category of tasks. Each component is associated to data objects it processes. The definition of components and data objects are based on research about planned system architectures of member states.

\subsection{User Profile}
Each member state provides its own user profile which manages the identity of a user. It enables him to create, delete and login to a profile, authenticate for administration services, communicate with institutions through an inbox and manage personal information and documents in a data wallet.

\subsection{Administration Portal}
The administration portal provides the user with a web-interface he can use to access his user profile and search for available administration services.

\subsection{Application Platform}
The application platform gives access to administration services by providing the user with a website he can use to fill in application forms and sent them to the responsible institutions. It is possible to prefill the form with personal data stored inside the user profile.

\subsection{Institution}
Institutions are the entities distributed all over the member state which eventually process the incoming applications and provide the users with solutions.

@@

\section{Integration Thoughts}

\subsection{OZG}

\subsection{IMP}

\chapter{Integration Architecture}

This chapter presents a message based integration architecture which enables access to OZG features of member states through an IMP. Multiple versions of an integration architecture are presented which fulfill increasingly complex requirements. Requirements are formulated as user scenarios which should be achievable through the IMP.
Each version is presented in the form of multiple flow charts, each describing sequential steps while carrying out a required scenario and a corresponding messaging infrastructure.

\section{Basic}

\subsection{Requirements}
In the first version of the integration architecture, users of the OSS provider should be able to
\begin{itemize}
    \item fill in an application
    \item authenticate
    \item receive and send messages
\end{itemize}

\subsection{Flow Charts}

\includegraphics[width=\textwidth]{Basic Integration Application.png}

\includegraphics[width=\textwidth]{Basic Integration Onboarding.png}

\subsection{Messaging Integration}

\section{Advanced}

\subsection{Requirements}

\subsection{Flow Charts}

\subsection{Messaging Integration}

\chapter{Integration Architecture Evaluation}

\section{Technology}

\section{Customer Example}

\section{Operating Manual}

@@

\begin{itemize}
     \item Expanding integration architecture with capabilities for OSS scenarios of different areas than online administration self-service
     \begin{itemize}
          \item online payment self-service (PayPal, psd2)
          \item online shopping self-service (Amazon)
          \item online health care self-service (DVG)
          \item online entertainment self-service (Netflix, YouTube, Spotify)
          \item online information / support self-service (StackOverflow)
     \end{itemize}
\end{itemize}

>>>>

          \vspace{0.5\baselineskip}
          {
               \huge
               \textbf{Integrating Identity Management Providers based on Online Zugangs Gesetz}
          }

@@

The result is variety of problems in management of digital identities \cite{IdentityCrisis}. Here are some examples:
\begin{itemize}
    \item Multiple SPs collect, use and share parts of identities which leads to distributed and fragmented identities.
    \item As a result of the distributed identities, risk of data breaches increases.
    \item Managing multiple use profiles is very inconvenient for users.
    \item It is often unclear who stores which data and for what purpose.
    \item SPs have an incentive to collect and share more user data than they need.
\end{itemize}

@@

\begin{itemize}
    \item OZG scenarios are based on documented digitalization efforts of administrative services in the context of the OZG and are for example the application for an administrative service or the communication with a governmental institution.
    \item The system architecture is based on documentation about architecture plans of member states.
    \item The functionalities of the IMP are based on a requirements analysis of OZG scenarios and additional research.
    \item The connector is defined based on functionalities the integration architecture requires from the IMP.
    \item The integration architecture is the main scientific contribution of this bachelor thesis. It is based on messaging patterns in order to utilize a combination of established and tested messaging solutions. In order to save investments it also reuses as many system components as possible and modifies as few system components as necessary.
\end{itemize}

The integration architecture ...

\chapter{Structure of Work}
The "Fundamentals" chapter explains terminology and basic concepts.

In the following chapter called "Identity Management System" the thesis analyzes requirements for identity management through the perspective of the user and through the perspective of service providers for the OZG. It is presented, how an identity management provider could solve current identity management problems and which challenges for an integration exist.

The chapter "Integration Proposal" first documents a possible IMP system and connector, based on the requirement analysis of the previous chapter. It then presents the integration architecture with iteratively increasing requirements through textual description, multiple flow diagrams and messaging architectures.

A "Solution Evaluation" analyzes benefits and problems of the proposed solution.

The "Outlook" will conclude the thesis by presenting possibilities for advanced integration architectures.

@@

\paragraph{Service Provider}
Service providers (SP) are entities like enterprises or organisations which make services accessible over the internet.

\paragraph{Online Self-Service}
Online self-service (OSS) describes a method used by Service Providers to make their services available to the user. The method is characterized by being available over the internet, requiring no direct human interaction but instead enabling the user to access services in a self-reliant way. The user is usually supported by a variety of software solutions.

\paragraph{Self-Service Tools}
Self-service tools are software solutions for customers to enable a online self-service experience. Depending on the use case, the tools can be transactional or informing. Informing tools help users to retrieve relevant information, often replacing human customer support. Transactional tools help users to interact with services in a persistent way to for example save personal data or trigger business processes.

@@

\paragraph{Digital Identity}
The digital identity, for simplicity called identity in the thesis, is the sum of all digital personal information. Each piece of personal information is an attribute. Attributes can be identifiers which are able uniquely identify an entity. It is also possible to use an aggregation of attributes as identifier.

@@

\paragraph{Partial Digital Identity}
A partial digital identity is a subset of an identity. Partial identities are commonly used by SPs to manage identity information which is relevant for them.

\paragraph{Identity Management}
Identity management is the creation, utilization / reading , updating and deletion of identities or partial identities. The possible utilization of identities depends on the system for management of identities. It could be for example authorization for a service or communication through an inbox.

\paragraph{Identity Management System}
Identity management systems are solutions which enable SPs and customers to manage identities or partial identities.
They usually provide the following functionalities an properties:
\begin{itemize}
    \item 
\end{itemize}

\paragraph{User Profile}
User profiles are one method for identity management. They are characterized by each SP providing a separate identity management system which often consist of an identity provider (IdP) for storing identities, a customer relation management system (CRM) for accessing identities internally and a website with online self-service tools for providing access to customers.

\section{Identity Management Provisioning (IMP)}
Identity management provisioning (IMP) is a method for identity management which is characterized by an identity management provider hosting an identity management system for "non-partial" identities. The identity management system provides one-stop online self-service for users and manages the storage of identities. SPs are provided access to the identities of the identity management system.

The following are functionalities of an IMP system in addition to those of conventional identity management systems:

\paragraph{Attribute Management}
It is common for identity management systems to enable users to manage a predetermined set of attributes. IMP systems however do not just manage partial identities and therefore enable users to manage any possible attribute of their identity. Users therefore can add, remove and modify any attribute.

As often, attributes of a digital identity are defined by service providers, they are also able to create new attributes or delete and modify existing ones, if approved by the user.

\paragraph{Online Self-Service}
Many attributes, especially those created by SPs, do not make sense to the user without context and my be heavily dependant on systems of a SP. Therefore, the IMP provides solutions for online self-service which supports the management of attributes.

\paragraph{Integration}
Service providers which use IMP systems as solution for identity management require access to its services and have to make their existing systems work with them. The IMP solution therefore provides interfaces which enable the SP to access services. As it is in the best interest of the IMP solution to integrate SPs, advanced integration methods reducing the integration effort for SPs can be provided.

\section{Online Access Law (OZG)}
In 2017 the German government passed the law for improvement of online access to administrative services (Online Zugangs Gesetz: OZG) which requires federal republic and member states to execute the following regulations until 2022 \cite{BMI:OZG_Wortlaut}:
\begin{enumerate}
    \item \textbf{Digital availability of administrative services} \\
    An administrative service is the electronic processing of administrative procedures which are available from outside the governmental institution.  As it is not clear which administrative services exactly are meant by the definition of the OZG, the BMI created a catalogue \cite{BMI:Verwaltungsleistungen}. The OZG requires these services to be digitally available. As a guideline to what is considered sufficient availability, the BMI defined a maturity model \cite{BMI:Digitale_Services}.
    \item \textbf{Digital access to administrative services through administration portals of a portal network} \\
    Federal republic, each member state and each commune must provide an administration portal. Portals of communes must be linked to the portal of the corresponding member state. Portals of federal republic and member states must be connected through a portal network. \cite{BMI:Portalverbund} Each portal must provide a "seek and find" feature, which enables users to find all administrative services provided by any administration portal \cite{Cotar:Drucksache_19/19089}. 
    \item \textbf{Interoperable user profiles for accessing administrative services} \\
    Federal republic and member states must provide user profiles which can be used to identify the corresponding person while requesting access to administrative services, to save personal information according to the once-only principle, to receive and send messages via a digital mailbox and to pay for services \cite{Cotar:Drucksache_19/19089}. The user profiles must be interoperable for every administration portal of the portal network.
\end{enumerate}

Execution of the OZG can be separated into two projects:

\paragraph{Digitalization}
Digitalization of administrative services focuses on accessibility towards users but not modernization of its internal execution by administrative institutions. The goal of digitalization in this case is, to make administrative services available towards a user in a digitized way:

A digitized administrative service can be accessed by a user through a website. The website is hosted either by the federal republic or a member state and is called "Administration Portal". Access is usually provided through an application form. The administrative service can be managed through a user profile which is provided by the federal republic or the member state. Management of an administrative service usually includes starting the service by sending in a form, communicating with responsible institutions through the inbox of the profile and receiving a result. The user profile can also enable users to upload documents to a data wallet and to save personal information for automatically filling in forms.

Digitalization of an administrative service is the modification of the underlying processes to incorporate the usage of the described features of the user profile and administration portal. In total, the BMI lists 575 relevant services, some of them provided by the federal republic, some by the member states and yet other by the communes \cite{BMI:Onlinezugangsgesetz}.

\paragraph{Networking}
The networking focuses on connecting governmental systems to make all digitized administrative services available for every user. This includes most importantly the connection of administration portals to a portal network through an online gateway and the interoperability of user profiles.

In order to save investments a method called "one for all" is used when hosting administrative services. One member state or the federal republic provide access to a service on their administration portal and distribute the requests to the responsible institutions "under the hood". As administration portals are connected through an "online gateway", each portal contains a search feature, which enables users to find all administrative services through any portal. Interoperable user profiles enable usage of each profile for management of administrative services on all portals.

\subsection{Administrative Service}
Unemployment benefit (Arbeitslosengeld II: AGII) is selected as an example for a digitized administrative service, because it has a high priority according to the "OZG-Informationsplattform" and is well documented.

The AGII is accessible through the "one for all" method through the administration portal of the federal republic. The digitalization of the service was done by the member state Nordrhein-Westfalen. The purpose of this service is to enable application for unemployment benefit and the result is an approval or denial by the responsible institution of the commune. The digitized process of this service enhances it to be manageable on an administration portal trough a user profile in the following way:

In order to access the service, a user must authenticate for an existing user profile or create one.

\subsection{System Architecture}
This subsection describes the system architecture of a member state relevant for the execution of the OZG.

\subsubsection{System Components}
The system architecture consists of the following system components where each component is responsible for processing a certain group of tasks:

\paragraph{User Profile}
Each member state provides its own user profile which manages the identity of a user. It enables him to create, delete and login to a profile, authenticate for administration services, communicate with institutions through an inbox and manage personal information and documents in a data wallet.

\paragraph{Administration Portal}
The administration portal provides the user with a web-interface he can use to access his user profile and search for available administration services.

\paragraph{Application Platform}
The application platform gives access to administration services by providing the user with a website he can use to fill in application forms and sent them to the responsible institutions. It is possible to prefill the form with personal data stored inside the user profile.

\paragraph{Institution}
Institutions are the entities distributed all over the member state which eventually process the incoming applications and provide the users with solutions.

\subsubsection{Data Objects}
The system architecture processes the following data objects which are associated to certain system components:

\chapter{Problem Analysis}

\section{Requirement Analysis}

\subsection{User Requirements}

\subsection{OZG Requirements}

@@

\subsubsection{Identity Management}

\textbf{Scenario Profile Management}
\begin{itemize}
    \item Create a user profile
    \item Delete a user profile
    \item Check existence of a user profile
\end{itemize}

\textbf{Scenario Identity verification}
\begin{itemize}
    \item Login to a user profile
    \item Provide multiple levels of security for identity verification
    \item Usage of a guest profile
\end{itemize}

\subsubsection{Request Management}

\textbf{Scenario Request Preparation}
\begin{itemize}
    \item Search for administration services
    \item Check necessity of a profile
    \item Check required level of identity verification
    \item Selection of institution responsible for processing the request (Specification of current location)
\end{itemize}

\textbf{Scenario Request Creation}
\begin{itemize}
    \item Filling in a form for an application
    \item Automated filling in of form with saved personal data
    \item Collaboration on application by multiple identities
\end{itemize}

\textbf{Scenario Request Delivery}
\begin{itemize}
    \item Transmission of an application to responsible institution
\end{itemize}

\textbf{Scenario Request Processing}
\begin{itemize}
    \item Period of validity of applications
    \item Notification of user about missing information or documents
    \item Transmission of missing information
    \item Notification of user about required preliminary administration services
    \item Communication through E-Mail
    \item Cancel an application
    \item Approvals of user to e.g. data protection or information transfer
    \item Modification request of application after transmission
    \item Notification of received application by institution
    \item Request status update by user
    \item Sending notification to confirm the reading of a message
    \item Notification of certain events to separate person e.g. parents
    \item Request of institution about explicit document
\end{itemize}

\textbf{Scenario Request Finalization}
\begin{itemize}
    \item Notification of outcome of process / application
    \item Objection of user to result of the process
    \item Access to signed digital formula of result of process
    \item Definition of dates for evens
\end{itemize}

\subsubsection{Data Management}

\textbf{Scenario Access Management}
\begin{itemize}
    \item Access to an application by multiple separate identities
    \item Sharing of documents saved in a wallet
\end{itemize}

\textbf{Scenario Data Consistency}
\begin{itemize}
    \item Period of validity of documents
    \item Profile data discrepancies between involved user profiles
\end{itemize}

\textbf{Scenario Data Accessibility}
\begin{itemize}
    \item Upload of e.g. documents and certificates
    \item Saving personal data entered in a form to the user profile
    \item Protocol of all processes accessible with information about interactions
\end{itemize}

\section{Solution with IMP}

\section{Integration Challenges}
The following challenges are a result of the functionalities an IMP system provides in addition to conventional identity management systems. The origin of the challenges is the interoperability of the IMP identity with multiple SPs. It is the purpose of the integration architecture to solve as many of these challenges as possible.

\paragraph{Data Mapping}
If multiple SPs and the user are able to add new attributes, there is the possibility of duplicate attributes with the same meaning but different name. It is also possible for SPs to utilize the same attribute but interpreting its meaning differently.

\paragraph{Identity Attributes}
Service providers are able to add attributes to an identity. It, however, is not clear which information should be added to an IMP system as part of an identity and which information should be stored by the individual SPs. One reason is, that service providers exist for which creation and utilization of personal information is a business model. For those SPs, the secrecy of certain types of personal information is important. One example would be information about product preferences of customers acquired by online retailers for usage with recommender systems.
A guideline could be, to only add attributes to the IMP system, which should be directly managed by users.

\paragraph{Online Self-Service}
SPs might add attributes to the identity of an IMP system which have very special meanings which are not self-explanatory. The attribute might also adhere to a special data format or be conditioned by other attributes of the identity. The modification of the attributes might also require interaction with the system architecture of an SP. In order for the attributes to stay valid, management through online self-service tools which are provided by the system architecture of an SP might be required.

In this case, the self-service tools should be accessible through the IMP systems in a user friendly way.

\paragraph{Attribute Access}
Attributes which were added by a SP might require restrictions towards the user. If for example a subscription status is saved as an attribute, the user should not be able to modify it without permission of the SP.

\chapter{Integration Proposal}
The bachelor thesis proposes an integration using a connector because:

@@

\section{Basic Integration Architecture}

\subsection{Version 1}

\subsubsection{Requirements}

\subsubsection{Flow Diagrams}

\includegraphics[width=15cm]{Basic Integration Onboarding.png}

\includegraphics[width=15cm]{Basic Integration Application.png}

\subsubsection{Messaging Architecture}

\subsection{Version 2}

\subsubsection{Requirements}

\subsubsection{Flow Diagrams}

\subsubsection{Messaging Architecture}

\chapter{Solution Evaluation}

\section{Conclusion}

@@

\section{Advanced Integration Architecture}
